
version alpha 0.0 
initialy designed functions
createAccount




version alpha 0.1 
The contract should be an ether pool (etherbase)
thus it should allow user charge their account by putting ether in to the contranct.
the first method to put ether in is the provide value when creating a user account.
A second way is to call topUp function to send ether to this contract and get some token.
By design, the token distributed by the contract should be at a constant exchange rate to ether.
currently, the rate is set to be 1 token = 1 wei which is the smallest ether unit.

A withdraw function is created corresponding to topUp function.
This function should allow user account to exchange their token back to ether in their ether address.
But the chellange is, when sending ether from the contract, the gas fee is to be paid by the sender, if the sender here is the message sender i.e. the user,
the user will pay for the gas, however, if the sender is considered as the contract itself, there will be a problem.
If the contract is charged gas for each transaction (the contract will loss at least 0.001 ether for each transaction according to current gas price),
the contract etherbase will fail due to too many withdraw transactions. The contract itself is not making any profit but will have to pay some fee due to users' transaction,
that's not fair.
Then an experiment should be held to examine how the ethereum network perform such a transaction from the contract with msg.sender a user to be the caller of the function.
0.001 ether = 10^15 wei which is a large amount of loss in terms of wei.
    experiment design:
    create the contract with external address A;
    create user account with external address B, charge 0.01 ether for token;
        expecting: the contract has 0.01 ether and address B pay 0.01 ether plus gas fee;
    address B call withdraw function to withdraw 0.01 ether;
        expecting: the contract send 0.01 ether to B and B pay the gas, resulting B receive 0.01 minus gas fee.
    A easy way to examine the behavior of the function (actually the contract convention) is to set a getter for the contract.
    top-up the contract first, suppose the contract possesses _amountA wei
        check the contract balance;
    withdraw _amountB wei by calling function withdraw as external address (user)
        check the contract balance;
        if the balance == _amountA - _amountB
            the transaction fee was paid by the msg.sender i.e. the user account.
        else
            the fee was paid by the contract

    If by convention the user will pay for calling a function that send ether from contract etherbase, 
    the withdraw function need not to have a mechanism to make the ether in contract intact
    
The contract shouldn't be paying that fee for transfering back. 
